---
title: "pruebas"
author: "Lidia Lopez"
date: "2022-08-26"
output: html_document
---

## Packages and functions

```{r package.call, echo = FALSE, warning = FALSE}

library(tidyverse)
library(readxl)
library(naniar)
library( Matrix)
library(lme4)
library(factoextra)
library(parameters)
library(merDeriv)
library(visreg)
library(performance)
library(see)

```

Read the new CSV:

```{r read_csv, warning= FALSE}

final_data <- read_csv("final_data.csv") 

```

Filter the interest variables for the models:

```{r select variables}

final_data1<- final_data %>% select( Site, Ringer, Ring, Species, Age, Sex, Data_origin, Wing, Tail, Tarsus, Weight, Bill,Fat, Muscle, Year, Month, Age2)

```



```{r as_factor}

final_data1$Month<-as.factor(final_data1$Month)
final_data1$Sex<-as.factor(final_data1$Sex)

```


Fit the lineal mixed model:


```{r change.species.name}

putLowerBar <- function(x) {
  new_value <-paste(unlist(strsplit(x," ")),collapse="_")[1]
  return(new_value)
}

final_data1$Species <- mapply(putLowerBar,final_data1$Species)

sort(unique(final_data1$Species))

for (Species in unique(final_data1$Species)) 
  {assign(paste0("df_",Species),final_data1[final_data1$Species==Species,])
}
```
 
##GLMM
Sex models

##Carduelis carduelis

```{r wing_carcar}
mod_wing_carcar<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Carduelis_carduelis)
ci_mod_wingcarcar<- confint(mod_wing_carcar)
summary(mod_wing_carcar)
show(ci_mod_wingcarcar)

```

Model asumptions:

```{r check the model}

visreg(mod_wing_carcar)
check_model(mod_wing_carcar)

```


```{r tarsus_carcar}

mod_Tarsus_carcar<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Carduelis_carduelis)
ci_mod_Tarsuscarcar<- confint(mod_Tarsus_carcar)
summary(mod_Tarsus_carcar)
show(ci_mod_Tarsuscarcar)

```

Model asumptions:

```{r check the model}

visreg(mod_Tarsus_carcar)
check_model(mod_Tarsus_carcar)

```


```{r weight_carcar}

mod_Weight_carcar<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Carduelis_carduelis)
ci_mod_Weightcarcar<- confint(mod_Weight_carcar)
summary(mod_Weight_carcar)
show(ci_mod_Weightcarcar)

```


Model asumptions:

```{r check the model}

visreg(mod_Weight_carcar)
check_model(mod_Weight_carcar)

```


##Chloris chloris


```{r wing_chlchl}
mod_wing_chlchl<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Chloris_chloris)
ci_mod_wingchlchl<- confint(mod_wing_chlchl)
summary(mod_wing_chlchl)
show(ci_mod_wingchlchl)

```


Model asumptions:

```{r check the model}

visreg(mod_wing_chlchl)
check_model(mod_wing_chlchl)

```


```{r tarsus_chlchl}

mod_Tarsus_chlchl<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Chloris_chloris)
ci_mod_Tarsuschlchl<- confint(mod_Tarsus_chlchl)
summary(mod_Tarsus_chlchl)
show(ci_mod_Tarsuschlchl)

```

Model asumptions:

```{r check the model}

visreg(mod_Tarsus_chlchl)
check_model(mod_Tarsus_chlchl)

```


```{r weight_chlchl}

mod_Weight_chlchl<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Chloris_chloris)
ci_mod_Weightchlchl<- confint(mod_Weight_chlchl)
summary(mod_Weight_chlchl)
show(ci_mod_Weightchlchl)

```


Model asumptions:

```{r check the model}

visreg(mod_Weight_chlchl)
check_model(mod_Weight_chlchl)

```



##Curruca melanocephala


```{r wing_curmel}
mod_wing_curmel<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Curruca_melanocephala)
ci_mod_wingcurmel<- confint(mod_wing_curmel)
summary(mod_wing_curmel)
show(ci_mod_wingcurmel)

```


Model asumptions:

```{r check the model}

visreg(mod_wing_curmel)
check_model(mod_wing_curmel)

```


```{r tarsus_curmel}

mod_Tarsus_curmel<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Curruca_melanocephala)
ci_mod_Tarsuscurmel<- confint(mod_Tarsus_curmel)
summary(mod_Tarsus_curmel)
show(ci_mod_Tarsuscurmel)

```

Model asumptions:

```{r check the model}

visreg(mod_Tarsus_curmel)
check_model(mod_Tarsus_curmel)

```



```{r weight_curmel}

mod_Weight_curmel<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Curruca_melanocephala)
ci_mod_Weightcurmel<- confint(mod_Weight_curmel)
summary(mod_Weight_curmel)
show(ci_mod_Weightcurmel)

```

Model asumptions:

```{r check the model}

visreg(mod_Weight_curmel)
check_model(mod_Weight_curmel)

```



##Ficedula hypoleuca


```{r wing_fichyp}
mod_wing_fichyp<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Ficedula_hypoleuca)
ci_mod_wingfichyp<- confint(mod_wing_fichyp)
summary(mod_wing_fichyp)
show(ci_mod_wingfichyp)

```

Model asumptions:

```{r check the model}

visreg(mod_wing_fichyp)
check_model(mod_wing_fichyp)

```


```{r tarsus_fichyp}

mod_Tarsus_fichyp<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Ficedula_hypoleuca)
ci_mod_Tarsusfichyp<- confint(mod_Tarsus_fichyp)
summary(mod_Tarsus_fichyp)
show(ci_mod_Tarsusfichyp)

```


Model asumptions:

```{r check the model}

visreg(mod_Tarsus_fichyp)
check_model(mod_Tarsus_fichyp)

```


```{r weight_fichyp}

mod_Weight_fichyp<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Ficedula_hypoleuca)
ci_mod_Weightfichyp<- confint(mod_Weight_fichyp)
summary(mod_Weight_fichyp)
show(ci_mod_Weightfichyp)

```

Model asumptions:

```{r check the model}

visreg(mod_Weight_fichyp)
check_model(mod_Weight_fichyp)

```


##Fringilla coelebs:



```{r wing_fricoe}
mod_wing_fricoe<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Fringilla_coelebs)
ci_mod_wingfricoe<- confint(mod_wing_fricoe)
summary(mod_wing_fricoe)
show(ci_mod_wingfricoe)

```


Model asumptions:

```{r check the model}

visreg(mod_wing_fricoe)
check_model(mod_wing_fricoe)

```


```{r tarsus_fricoe}

mod_Tarsus_fricoe<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Fringilla_coelebs)
ci_mod_Tarsusfricoe<- confint(mod_Tarsus_fricoe)
summary(mod_Tarsus_fricoe)
show(ci_mod_Tarsusfricoe)

```

Model asumptions:

```{r check the model}

visreg(mod_Tarsus_fricoe)
check_model(mod_Tarsus_fricoe)

```

```{r weight_fricoe}

mod_Weight_fricoe<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Fringilla_coelebs)
ci_mod_Weightfricoe<- confint(mod_Weight_fricoe)
summary(mod_Weight_fricoe)
show(ci_mod_Weightfricoe)

```

Model asumptions:

```{r check the model}

visreg(mod_Weight_fricoe)
check_model(mod_Weight_fricoe)



```

##Parus major


```{r wing_parmaj}
mod_wing_parmaj<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Parus_major)
ci_mod_wingparmaj<- confint(mod_wing_parmaj)
summary(mod_wing_parmaj)
show(ci_mod_wingparmaj)

```

Model asumptions:

```{r check the model}

visreg(mod_wing_parmaj)
check_model(mod_wing_parmaj)



```



```{r tarsus_parmaj}

mod_Tarsus_parmaj<- lm(formula = Tarsus ~ Year + Age2 + Sex, data= df_Parus_major)
ci_mod_Tarsusparmaj<- confint(mod_Tarsus_parmaj)
summary(mod_Tarsus_parmaj)
show(ci_mod_Tarsusparmaj)

```

Model asumptions:

```{r check the model}

visreg(mod_Tarsus_parmaj)
check_model(mod_Tarsus_parmaj)



```

```{r weight_parmaj}

mod_Weight_parmaj<- lm(formula = Weight ~ Year + Age2 + Sex + Month , data= df_Parus_major)
ci_mod_Weightparmaj<- confint(mod_Weight_parmaj)
summary(mod_Weight_parmaj)
show(ci_mod_Weightparmaj)

```

Model asumptions:

```{r check the model}

visreg(mod_Weight_parmaj)
check_model(mod_Weight_parmaj)



```

##Phylloscopus collybita

```{r wing_phycol}
mod_wing_phycol<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Phylloscopus_collybita)
ci_mod_wingphycol<- confint(mod_wing_phycol)
 summary(mod_wing_phycol)
 show(ci_mod_wingphycol)

```


Model asumptions:

```{r check the model}

visreg(mod_wing_phycol)
check_model(mod_wing_phycol)



```


```{r tarsus_phycol}

mod_Tarsus_phycol<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Phylloscopus_collybita)
 ci_mod_Tarsusphycol<- confint(mod_Tarsus_phycol)
 summary(mod_Tarsus_phycol)
 show(ci_mod_Tarsusphycol)

```

Model asumptions:

```{r check the model}

visreg(mod_Tarsus_phycol)
check_model(mod_Tarsus_phycol)



```

```{r weight_phycol}

mod_Weight_phycol<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Phylloscopus_collybita)
ci_mod_Weightphycol<- confint(mod_Weight_phycol)
summary(mod_Weight_phycol)
show(ci_mod_Weightphycol)

```

Model asumptions:

```{r check the model}

visreg(mod_Weight_phycol)
check_model(mod_Weight_phycol)



```

##Serinus serinus

```{r wing_serser}
mod_wing_serser<- lmer(formula = Wing ~ Year + Age2 + Sex + Month +(1|Ringer) + (1|Site), data= df_Serinus_serinus)
ci_mod_wingserser<- confint(mod_wing_serser)
summary(mod_wing_serser)
show(ci_mod_wingserser)

```


Model asumptions:

```{r check the model}

visreg(mod_wing_serser)
check_model(mod_wing_serser)



```


```{r tarsus_serser}

mod_Tarsus_serser<- lm(formula = Tarsus ~ Year + Age2 + Sex, data= df_Serinus_serinus)
ci_mod_Tarsusserser<- confint(mod_Tarsus_serser)
summary(mod_Tarsus_serser)
show(ci_mod_Tarsusserser)

```

Model asumptions:

```{r check the model}

visreg(mod_Tarsus_serser)
check_model(mod_Tarsus_serser)



```

```{r weight_serser}

mod_Weight_serser<- lm(formula = Weight ~ Year + Age2 + Sex + Month, data= df_Serinus_serinus)
ci_mod_Weightserser<- confint(mod_Weight_serser)
summary(mod_Weight_serser)
show(ci_mod_Weightserser)

```

Model asumptions:

```{r check the model}

visreg(mod_Weight_serser)
check_model(mod_Weight_serser)


```

##Sylvia atricapilla

```{r wing_sylatr}

mod_wing_sylatr<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Sylvia_atricapilla)
ci_mod_wingsylatr<- confint(mod_wing_sylatr)
summary(mod_wing_sylatr)
show(ci_mod_wingsylatr)

```

Model asumptions:

```{r check the model}

visreg(mod_wing_sylatr)
check_model(mod_wing_sylatr)



```

```{r tarsus_sylatr}

mod_Tarsus_sylatr<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Sylvia_atricapilla)
ci_mod_Tarsussylatr<- confint(mod_Tarsus_sylatr)
summary(mod_Tarsus_sylatr)
show(ci_mod_Tarsussylatr)

```

Model asumptions:

```{r check the model}

visreg(mod_Tarsus_sylatr)
check_model(mod_Tarsus_sylatr)



```

```{r weight_sylatr}

mod_Weight_sylatr<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Sylvia_atricapilla)
ci_mod_Weightsylatr<- confint(mod_Weight_sylatr)
summary(mod_Weight_sylatr)
show(ci_mod_Weightsylatr)

```

Model asumptions:

```{r check the model}

visreg(mod_Weight_sylatr)
check_model(mod_Weight_sylatr)



```

##Sylvia communis

```{r wing_sylcom}
mod_wing_sylcom<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Curruca_communis)
ci_mod_wingsylcom<- confint(mod_wing_sylcom)
summary(mod_wing_sylcom)
show(ci_mod_wingsylcom)

```

Model asumptions:

```{r check the model}

visreg(mod_wing_sylcom)
check_model(mod_wing_sylcom)



```


```{r tarsus_sylcom}

mod_Tarsus_sylcom<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Curruca_communis)
ci_mod_Tarsussylcom<- confint(mod_Tarsus_sylcom)
summary(mod_Tarsus_sylcom)
show(ci_mod_Tarsussylcom)

```
Model asumptions:

```{r check the model}

visreg(mod_Tarsus_sylcom)
check_model(mod_Tarsus_sylcom)



```


```{r weight_sylcom}

mod_Weight_sylcom<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Curruca_communis)
ci_mod_Weightsylcom<- confint(mod_Weight_sylcom)
summary(mod_Weight_sylcom)
show(ci_mod_Weightsylcom)

```

Model asumptions:

```{r check the model}

visreg(mod_Weight_sylcom)
check_model(mod_Weight_sylcom)



```


##Turdus merula

```{r wing_turmer}
mod_wing_turmer<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Turdus_merula)
ci_mod_wingturmer<- confint(mod_wing_turmer)
summary(mod_wing_turmer)
show(ci_mod_wingturmer)

```


Model asumptions:

```{r check the model}

visreg(mod_wing_turmer)
check_model(mod_wing_turmer)


```

```{r tarsus_turmer}

mod_Tarsus_turmer<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Turdus_merula)
ci_mod_Tarsusturmer<- confint(mod_Tarsus_turmer)
summary(mod_Tarsus_turmer)
show(ci_mod_Tarsusturmer)

```


Model asumptions:

```{r check the model}

visreg(mod_Tarsus_turmer)
check_model(mod_Tarsus_turmer)


```

```{r weight_turmer}

mod_Weight_turmer<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Turdus_merula)
ci_mod_Weightturmer<- confint(mod_Weight_turmer)
summary(mod_Weight_turmer)
show(ci_mod_Weightturmer)

```


Model asumptions:

```{r check the model}

visreg(mod_Weight_turmer)
check_model(mod_Weight_turmer)


```


No sex models:

##Erithacus rubecula



```{r wing_erirub}
mod_wing_erirub<- lmer(formula = Wing ~ Year + Age2 +  Month + (1|Ringer) + (1|Site), data= df_Erithacus_rubecula)
ci_mod_wingerirub<- confint(mod_wing_erirub)
summary(mod_wing_erirub)
show(ci_mod_wingerirub)

```



Model asumptions:

```{r check the model}

visreg(mod_wing_erirub)
check_model(mod_wing_erirub)


```



```{r tarsus_erirub}

mod_Tarsus_erirub<- lmer(formula = Tarsus ~ Year + Age2 + (1|Ringer) + (1|Site), data= df_Erithacus_rubecula)
ci_mod_Tarsuserirub<- confint(mod_Tarsus_erirub)
summary(mod_Tarsus_erirub)
show(ci_mod_Tarsuserirub)

```


Model asumptions:

```{r check the model}

visreg(mod_Tarsus_erirub)
check_model(mod_Tarsus_erirub)


```



```{r weight_erirub}

mod_Weight_erirub<- lmer(formula = Weight ~ Year + Age2 + Month  + (1|Site), data= df_Erithacus_rubecula)
ci_mod_Weighterirub<- confint(mod_Weight_erirub)
summary(mod_Weight_erirub)
show(ci_mod_Weighterirub)

```


Model asumptions:

```{r check the model}

visreg(mod_Weight_erirub)
check_model(mod_Weight_erirub)


```



##Sylvia borin

```{r wing_sylbor}
mod_wing_sylbor<- lmer(formula = Wing ~ Year + Age2 +  Month + (1|Ringer) + (1|Site), data= df_Sylvia_borin)
ci_mod_Wingsylbor<- confint(mod_wing_sylbor)
summary(mod_Wing_sylbor)
show(ci_mod_Wingsylbor)

```


Model asumptions:

```{r check the model}

visreg(mod_wing_sylbor)
check_model(mod_wing_sylbor)


```

```{r tarsus_sylbor}

mod_Tarsus_sylbor<- lmer(formula = Tarsus ~ Year + Age2 + (1|Ringer) + (1|Site), data= df_Sylvia_borin)
ci_mod_Tarsussylbor<- confint(mod_Tarsus_sylbor)
summary(mod_Tarsus_sylbor)
show(ci_mod_Tarsussylbor)

```

Model asumptions:

```{r check the model}

visreg(mod_Tarsus_sylbor)
check_model(mod_Tarsus_sylbor)


```

```{r weight_sylbor}

mod_Weight_sylbor<- lmer(formula = Weight ~ Year + Age2 + Month  + (1|Site), data= df_Sylvia_borin)
ci_mod_Weightsylbor<- confint(mod_Weight_sylbor)
summary(mod_Weight_sylbor)
show(ci_mod_Weightsylbor)

```

Model asumptions:

```{r check the model}

visreg(mod_Weight_sylbor)
check_model(mod_Weight_sylbor)


```

##Turdus philomelos

```{r wing_turphi}
mod_wing_turphi<- lmer(formula = Wing ~ Year + Age2 +  Month + (1|Ringer) + (1|Site), data= df_Turdus_philomelos)
ci_mod_wingturphi<- confint(mod_wing_turphi)
summary(mod_wing_turphi)
show(ci_mod_wingturphi)

```

Model asumptions:

```{r check the model}

visreg(mod_Weight_turphi)
check_model(mod_Weight_turphi)



```



Model asumptions:

```{r check the model}

visreg(mod_wing_turphi)
check_model(mod_wing_turphi)


```


```{r tarsus_turphi}

mod_Tarsus_turphi<- lm(formula = Tarsus ~ Year + Age2, data= df_Turdus_philomelos)
ci_mod_Tarsusturphi<- confint(mod_Tarsus_turphi)
summary(mod_Tarsus_turphi)
show(ci_mod_Tarsusturphi)

```


Model asumptions:

```{r check the model}

visreg(mod_Tarsus_turphi)
check_model(mod_Tarsus_turphi)



```

```{r weight_turphi}

mod_Weight_turphi<- lmer(formula = Weight ~ Year + Age2 + Month  + (1|Site), data= df_Turdus_philomelos)
ci_mod_Weightturphi<- confint(mod_Weight_turphi)
summary(mod_Weight_turphi)
show(ci_mod_Weightturphi)

```


Model asumptions:

```{r check the model}

visreg(mod_Weight_turphi)
check_model(mod_Weight_turphi)


```

