---
title: "Untitled"
author: "Lidia Lopez"
date: "2022-09-05"
output: html_document
---

## Packages and functions

```{r package.call, echo = FALSE, warning = FALSE}

library(tidyverse)
library(readxl)
library(naniar)
library( Matrix)
library(lme4)
library(factoextra)
library(parameters)
library(merDeriv)
library(visreg)
library(performance)
library(see)

```


Read the new CSV:

```{r read_csv, warning= FALSE}

final_data <- read_csv("final_data.csv") 

```



Filter the interest variables for the models:

```{r select variables}

final_data1<- final_data %>% select( Site, Ringer, Ring, Species, Age, Sex, Data_origin, Wing, Tail, Tarsus, Weight, Bill,Fat, Muscle, Year, Month, Age2)

```



```{r as_factor}

final_data1$Month<-as.factor(final_data1$Month)
final_data1$Sex<-as.factor(final_data1$Sex)

```

```{r change.species.name}

putLowerBar <- function(x) {
  new_value <-paste(unlist(strsplit(x," ")),collapse="_")[1]
  return(new_value)
}

final_data1$Species <- mapply(putLowerBar,final_data1$Species)

sort(unique(final_data1$Species))

for (Species in unique(final_data1$Species)) 
  {assign(paste0("df_",Species),final_data1[final_data1$Species==Species,])
}
```

##GLMM
Sex models

##Carduelis carduelis

```{r wing_carcar}
mod_wing_carcar<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Carduelis_carduelis)

```

```{r tarsus_carcar}

mod_Tarsus_carcar<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Carduelis_carduelis)

```


```{r weight_carcar}

mod_Weight_carcar<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Carduelis_carduelis)

```


AIC:

```{r AIC comprobations}
mod_wing_carcar2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Carduelis_carduelis)

mod_wing_carcar3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Carduelis_carduelis)

mod_wing_carcar4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Carduelis_carduelis)


AIC(mod_wing_carcar,mod_wing_carcar2,mod_wing_carcar3,mod_wing_carcar4)
```



```{r AIC comprobations}
mod_tarsus_carcar2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Carduelis_carduelis)

mod_tarsus_carcar3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Carduelis_carduelis)

mod_tarsus_carcar4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Carduelis_carduelis)


AIC(mod_Tarsus_carcar,mod_tarsus_carcar2,mod_tarsus_carcar3,mod_tarsus_carcar4)
```


```{r AIC comprobations}
mod_Weight_carcar2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Carduelis_carduelis)

AIC(mod_Weight_carcar,mod_Weight_carcar2)
```


##Chloris chloris

```{r wing_chlchl}
mod_wing_chlchl<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Chloris_chloris)

```


```{r tarsus_chlchl}

mod_Tarsus_chlchl<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Chloris_chloris)

```

```{r weight_chlchl}

mod_Weight_chlchl<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Chloris_chloris)

```


AIC:

```{r AIC comprobations}
mod_wing_chlchl2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Chloris_chloris)

mod_wing_chlchl3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Chloris_chloris)

mod_wing_chlchl4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Chloris_chloris)


AIC(mod_wing_chlchl,mod_wing_chlchl2,mod_wing_chlchl3,mod_wing_chlchl4)
```



```{r AIC comprobations}
mod_tarsus_chlchl2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Chloris_chloris)

mod_tarsus_chlchl3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Chloris_chloris)

mod_tarsus_chlchl4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Chloris_chloris)


AIC(mod_Tarsus_chlchl,mod_tarsus_chlchl2,mod_tarsus_chlchl3,mod_tarsus_chlchl4)
```


```{r AIC comprobations}
mod_Weight_chlchl2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Chloris_chloris)

AIC(mod_Weight_chlchl,mod_Weight_chlchl2)
```


##Curruca melanocephala


```{r wing_curmel}
mod_wing_curmel<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Curruca_melanocephala)

```


```{r tarsus_curmel}

mod_Tarsus_curmel<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Curruca_melanocephala)

```

```{r weight_curmel}

mod_Weight_curmel<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Curruca_melanocephala)

```

AIC:

```{r AIC comprobations}
mod_wing_curmel2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Curruca_melanocephala)

mod_wing_curmel3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Curruca_melanocephala)

mod_wing_curmel4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Curruca_melanocephala)


AIC(mod_wing_curmel,mod_wing_curmel2,mod_wing_curmel3,mod_wing_curmel4)
```



```{r AIC comprobations}
mod_tarsus_curmel2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Curruca_melanocephala)

mod_tarsus_curmel3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Curruca_melanocephala)

mod_tarsus_curmel4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Curruca_melanocephala)


AIC(mod_Tarsus_curmel,mod_tarsus_curmel2,mod_tarsus_curmel3,mod_tarsus_curmel4)
```


```{r AIC comprobations}
mod_Weight_curmel2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Curruca_melanocephala)

AIC(mod_Weight_curmel,mod_Weight_curmel2)
```


##Ficedula hypoleuca


```{r wing_fichyp}
mod_wing_fichyp<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Ficedula_hypoleuca)

```


```{r tarsus_fichyp}

mod_Tarsus_fichyp<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Ficedula_hypoleuca)

```



```{r weight_fichyp}

mod_Weight_fichyp<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Ficedula_hypoleuca)

```


AIC:

```{r AIC comprobations}
mod_wing_fichyp2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Ficedula_hypoleuca)

mod_wing_fichyp3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Ficedula_hypoleuca)

mod_wing_fichyp4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Ficedula_hypoleuca)


AIC(mod_wing_fichyp,mod_wing_fichyp2,mod_wing_fichyp3,mod_wing_fichyp4)
```


```{r AIC comprobations}
mod_tarsus_fichyp2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Ficedula_hypoleuca)

mod_tarsus_fichyp3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Ficedula_hypoleuca)

mod_tarsus_fichyp4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Ficedula_hypoleuca)


AIC(mod_Tarsus_fichyp,mod_tarsus_fichyp2,mod_tarsus_fichyp3,mod_tarsus_fichyp4)
```


```{r AIC comprobations}
mod_Weight_fichyp2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Ficedula_hypoleuca)

AIC(mod_Weight_fichyp,mod_Weight_fichyp2)
```


##Fringilla coelebs:


```{r wing_fricoe}
mod_wing_fricoe<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Fringilla_coelebs)

```



```{r tarsus_fricoe}

mod_Tarsus_fricoe<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Fringilla_coelebs)

```


```{r weight_fricoe}

mod_Weight_fricoe<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Fringilla_coelebs)

```

AIC:

```{r AIC comprobations}
mod_wing_fricoe2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Fringilla_coelebs)

mod_wing_fricoe3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Fringilla_coelebs)

mod_wing_fricoe4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Fringilla_coelebs)


AIC(mod_wing_fricoe,mod_wing_fricoe2,mod_wing_fricoe3,mod_wing_fricoe4)
```


```{r AIC comprobations}
mod_tarsus_fricoe2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Fringilla_coelebs)

mod_tarsus_fricoe3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Fringilla_coelebs)

mod_tarsus_fricoe4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Fringilla_coelebs)


AIC(mod_Tarsus_fricoe,mod_tarsus_fricoe2,mod_tarsus_fricoe3,mod_tarsus_fricoe4)
```


```{r AIC comprobations}
mod_Weight_fricoe2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Fringilla_coelebs)

AIC(mod_Weight_fricoe,mod_Weight_fricoe2)
```

##Parus major


```{r wing_parmaj}
mod_wing_parmaj<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Parus_major)


```



```{r tarsus_parmaj}

mod_Tarsus_parmaj<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Parus_major)

```

```{r weight_parmaj}

mod_Weight_parmaj<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Parus_major)

```

AIC:

```{r AIC comprobations}
mod_wing_parmaj2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Parus_major)

mod_wing_parmaj3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Parus_major)

mod_wing_parmaj4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Parus_major)


AIC(mod_wing_parmaj,mod_wing_parmaj2,mod_wing_parmaj3,mod_wing_parmaj4)
```



```{r AIC comprobations}
mod_tarsus_parmaj2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Parus_major)

mod_tarsus_parmaj3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Parus_major)

mod_tarsus_parmaj4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Parus_major)


AIC(mod_Tarsus_parmaj,mod_tarsus_parmaj2,mod_tarsus_parmaj3,mod_tarsus_parmaj4)
```


```{r AIC comprobations}
mod_Weight_parmaj2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Parus_major)

AIC(mod_Weight_parmaj,mod_Weight_parmaj2)
```

##Phylloscopus collybita

```{r wing_phycol}
mod_wing_phycol<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Phylloscopus_collybita)

```


```{r tarsus_phycol}

mod_Tarsus_phycol<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Phylloscopus_collybita)

```


```{r weight_phycol}

mod_Weight_phycol<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Phylloscopus_collybita)

```


AIC:

```{r AIC comprobations}
mod_wing_phycol2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Phylloscopus_collybita)

mod_wing_phycol3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Phylloscopus_collybita)

mod_wing_phycol4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Phylloscopus_collybita)


AIC(mod_wing_phycol,mod_wing_phycol2,mod_wing_phycol3,mod_wing_phycol4)
```



```{r AIC comprobations}
mod_tarsus_phycol2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Phylloscopus_collybita)

mod_tarsus_phycol3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Phylloscopus_collybita)

mod_tarsus_phycol4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Phylloscopus_collybita)


AIC(mod_Tarsus_phycol,mod_tarsus_phycol2,mod_tarsus_phycol3,mod_tarsus_phycol4)
```


```{r AIC comprobations}
mod_Weight_phycol2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Phylloscopus_collybita)

AIC(mod_Weight_phycol,mod_Weight_phycol2)
```

##Serinus serinus

```{r wing_serser}
mod_wing_serser<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Serinus_serinus)

```


```{r tarsus_serser}

mod_Tarsus_serser<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Serinus_serinus)

```


```{r weight_serser}

mod_Weight_serser<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Serinus_serinus)

```

AIC:

```{r AIC comprobations}
mod_wing_serser2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Serinus_serinus)

mod_wing_serser3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Serinus_serinus)

mod_wing_serser4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Serinus_serinus)


AIC(mod_wing_serser,mod_wing_serser2,mod_wing_serser3,mod_wing_serser4)
```



```{r AIC comprobations}
mod_tarsus_serser2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Serinus_serinus)

mod_tarsus_serser3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Serinus_serinus)

mod_tarsus_serser4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Serinus_serinus)


AIC(mod_Tarsus_serser,mod_tarsus_serser2,mod_tarsus_serser3,mod_tarsus_serser4)
```


```{r AIC comprobations}
mod_Weight_serser2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Serinus_serinus)

AIC(mod_Weight_serser,mod_Weight_serser2)
```

##Sylvia atricapilla

```{r wing_sylatr}
mod_wing_sylatr<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Sylvia_atricapilla)

```


```{r tarsus_sylatr}

mod_Tarsus_sylatr<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Sylvia_atricapilla)

```


```{r weight_sylatr}

mod_Weight_sylatr<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Sylvia_atricapilla)

```

AIC:

```{r AIC comprobations}
mod_wing_sylatr2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Sylvia_atricapilla)

mod_wing_sylatr3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Sylvia_atricapilla)

mod_wing_sylatr4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Sylvia_atricapilla)


AIC(mod_wing_sylatr,mod_wing_sylatr2,mod_wing_sylatr3,mod_wing_sylatr4)
```



```{r AIC comprobations}
mod_tarsus_sylatr2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Sylvia_atricapilla)

mod_tarsus_sylatr3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Sylvia_atricapilla)

mod_tarsus_sylatr4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Sylvia_atricapilla)


AIC(mod_Tarsus_sylatr,mod_tarsus_sylatr2,mod_tarsus_sylatr3,mod_tarsus_sylatr4)
```


```{r AIC comprobations}
mod_Weight_sylatr2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Sylvia_atricapilla)

AIC(mod_Weight_sylatr,mod_Weight_sylatr2)
```



##Sylvia communis

```{r wing_sylcom}
mod_wing_sylcom<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Sylvia_communis)

```

```{r tarsus_sylcom}

mod_Tarsus_sylcom<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Sylvia_communis)

```


```{r weight_sylcom}

mod_Weight_sylcom<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Sylvia_communis)

```

AIC:

```{r AIC comprobations}
mod_wing_sylcom2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Sylvia_communis)

mod_wing_sylcom3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Sylvia_communis)

mod_wing_sylcom4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Sylvia_communis)


AIC(mod_wing_sylcom,mod_wing_sylcom2,mod_wing_sylcom3,mod_wing_sylcom4)
```



```{r AIC comprobations}
mod_tarsus_sylcom2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Sylvia_communis)

mod_tarsus_sylcom3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Sylvia_communis)

mod_tarsus_sylcom4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Sylvia_communis)


AIC(mod_Tarsus_sylcom,mod_tarsus_sylcom2,mod_tarsus_sylcom3,mod_tarsus_sylcom4)
```


```{r AIC comprobations}
mod_Weight_sylcom2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Sylvia_communis)

AIC(mod_Weight_sylcom,mod_Weight_sylcom2)
```



##Turdus merula

```{r wing_turmer}
mod_wing_turmer<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer) + (1|Site), data= df_Turdus_merula)

```


```{r tarsus_turmer}

mod_Tarsus_turmer<- lmer(formula = Tarsus ~ Year + Age2 + Sex +(1|Ringer) + (1|Site), data= df_Turdus_merula)

```


```{r weight_turmer}

mod_Weight_turmer<- lmer(formula = Weight ~ Year + Age2 + Sex + Month  + (1|Site), data= df_Turdus_merula)

```


AIC:

```{r AIC comprobations}
mod_wing_turmer2<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Ringer), data= df_Turdus_merula)

mod_wing_turmer3<- lmer(formula = Wing ~ Year + Age2 + Sex + Month + (1|Site), data= df_Turdus_merula)

mod_wing_turmer4<- lm(formula = Wing ~ Year + Age2 + Sex + Month, data= df_Turdus_merula)


AIC(mod_wing_turmer,mod_wing_turmer2,mod_wing_turmer3,mod_wing_turmer4)
```



```{r AIC comprobations}
mod_tarsus_turmer2<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Ringer), data= df_Turdus_merula)

mod_tarsus_turmer3<- lmer(formula = Tarsus ~ Year + Age2 + Sex + (1|Site), data= df_Turdus_merula)

mod_tarsus_turmer4<- lm(formula = Tarsus ~ Year + Age2 + Sex , data= df_Turdus_merula)


AIC(mod_Tarsus_turmer,mod_tarsus_turmer2,mod_tarsus_turmer3,mod_tarsus_turmer4)
```


```{r AIC comprobations}
mod_Weight_turmer2<- lm(formula = Weight ~ Year + Age2 + Sex+ Month, data= df_Turdus_merula)

AIC(mod_Weight_turmer,mod_Weight_turmer2)
```

No sex models:

##Erithacus rubecula

```{r wing_erirub}
mod_wing_erirub<- lmer(formula = Wing ~ Year + Age2 +  Month + (1|Ringer) + (1|Site), data= df_Erithacus_rubecula)

```


```{r tarsus_erirub}

mod_Tarsus_erirub<- lmer(formula = Tarsus ~ Year + Age2 + (1|Ringer) + (1|Site), data= df_Erithacus_rubecula)

```


```{r weight_erirub}

mod_Weight_erirub<- lmer(formula = Weight ~ Year + Age2 + Month  + (1|Site), data= df_Erithacus_rubecula)

```


AIC:

```{r AIC comprobations}
mod_wing_erirub2<- lmer(formula = Wing ~ Year + Age2 + Month + (1|Ringer), data= df_Erithacus_rubecula)

mod_wing_erirub3<- lmer(formula = Wing ~ Year + Age2 + Month + (1|Site), data= df_Erithacus_rubecula)

mod_wing_erirub4<- lm(formula = Wing ~ Year + Age2 + Month, data= df_Erithacus_rubecula)


AIC(mod_wing_erirub,mod_wing_erirub2,mod_wing_erirub3,mod_wing_erirub4)
```



```{r AIC comprobations}
mod_tarsus_erirub2<- lmer(formula = Tarsus ~ Year + Age2 + (1|Ringer), data= df_Erithacus_rubecula)

mod_tarsus_erirub3<- lmer(formula = Tarsus ~ Year + Age2 + (1|Site), data= df_Erithacus_rubecula)

mod_tarsus_erirub4<- lm(formula = Tarsus ~ Year + Age2 , data= df_Erithacus_rubecula)


AIC(mod_Tarsus_erirub,mod_tarsus_erirub2,mod_tarsus_erirub3,mod_tarsus_erirub4)
```


```{r AIC comprobations}
mod_Weight_erirub2<- lm(formula = Weight ~ Year + Age2 + Month, data= df_Erithacus_rubecula)

AIC(mod_Weight_erirub,mod_Weight_erirub2)
```



##Sylvia borin

```{r wing_sylbor}
mod_wing_sylbor<- lmer(formula = Wing ~ Year + Age2 +  Month + (1|Ringer) + (1|Site), data= df_Sylvia_borin)

```


```{r tarsus_sylbor}

mod_Tarsus_sylbor<- lmer(formula = Tarsus ~ Year + Age2 + (1|Ringer) + (1|Site), data= df_Sylvia_borin)

```


```{r weight_sylbor}

mod_Weight_sylbor<- lmer(formula = Weight ~ Year + Age2 + Month  + (1|Site), data= df_Sylvia_borin)

```

AIC:

```{r AIC comprobations}
mod_wing_sylbor2<- lmer(formula = Wing ~ Year + Age2 + Month + (1|Ringer), data= df_Sylvia_borin)

mod_wing_sylbor3<- lmer(formula = Wing ~ Year + Age2 + Month + (1|Site), data= df_Sylvia_borin)

mod_wing_sylbor4<- lm(formula = Wing ~ Year + Age2 + Month, data= df_Sylvia_borin)


AIC(mod_wing_sylbor,mod_wing_sylbor2,mod_wing_sylbor3,mod_wing_sylbor4)
```



```{r AIC comprobations}
mod_tarsus_sylbor2<- lmer(formula = Tarsus ~ Year + Age2 + (1|Ringer), data= df_Sylvia_borin)

mod_tarsus_sylbor3<- lmer(formula = Tarsus ~ Year + Age2 + (1|Site), data= df_Sylvia_borin)

mod_tarsus_sylbor4<- lm(formula = Tarsus ~ Year + Age2 , data= df_Sylvia_borin)


AIC(mod_Tarsus_sylbor,mod_tarsus_sylbor2,mod_tarsus_sylbor3,mod_tarsus_sylbor4)
```


```{r AIC comprobations}
mod_Weight_sylbor2<- lm(formula = Weight ~ Year + Age2 + Month, data= df_Sylvia_borin)

AIC(mod_Weight_sylbor,mod_Weight_sylbor2)
```



##Turdus philomelos

```{r wing_turphi}
mod_wing_turphi<- lmer(formula = Wing ~ Year + Age2 +  Month + (1|Ringer) + (1|Site), data= df_Turdus_philomelos)

```


```{r tarsus_turphi}

mod_Tarsus_turphi<- lmer(formula = Tarsus ~ Year + Age2 + (1|Ringer) + (1|Site), data= df_Turdus_philomelos)

```


```{r weight_turphi}

mod_Weight_turphi<- lmer(formula = Weight ~ Year + Age2 + Month  + (1|Site), data= df_Turdus_philomelos)

```

AIC:

```{r AIC comprobations}
mod_wing_turphi2<- lmer(formula = Wing ~ Year + Age2 + Month + (1|Ringer), data= df_Turdus_philomelos)

mod_wing_turphi3<- lmer(formula = Wing ~ Year + Age2 + Month + (1|Site), data= df_Turdus_philomelos)

mod_wing_turphi4<- lm(formula = Wing ~ Year + Age2 + Month, data= df_Turdus_philomelos)


AIC(mod_wing_turphi,mod_wing_turphi2,mod_wing_turphi3,mod_wing_turphi4)
```



```{r AIC comprobations}
mod_tarsus_turphi2<- lmer(formula = Tarsus ~ Year + Age2 + (1|Ringer), data= df_Turdus_philomelos)

mod_tarsus_turphi3<- lmer(formula = Tarsus ~ Year + Age2 + (1|Site), data= df_Turdus_philomelos)

mod_tarsus_turphi4<- lm(formula = Tarsus ~ Year + Age2 , data= df_Turdus_philomelos)


AIC(mod_Tarsus_turphi,mod_tarsus_turphi2,mod_tarsus_turphi3,mod_tarsus_turphi4)
```


```{r AIC comprobations}
mod_Weight_turphi2<- lm(formula = Weight ~ Year + Age2 + Month, data= df_Turdus_philomelos)

AIC(mod_Weight_turphi,mod_Weight_turphi2)
```

